---
title: "LONGO: Long gene expression as a metric for neuronal identity"
author: "Alex Paul"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## LONGO

LONGO is designed to have two different uses. One through a shiny interface and another through R. Both of the results of these uses of the program are the same. The shiny interface will allow the user to alter certain variables in the analysis to see how they will affect the final result. This can be useful when interpreting new data. 

LONGO is designed to take in a data file, take the gene identifier to get the gene name and length. Occasionally there will be multiple probes going to a single gene. LONGO can handle this in two different ways. The default way is by only keeping the probe that has the highest overall expression values. The other option is to get the mean expression values. If a read has no identified gene name or length in biomaRt, the read is removed. 

After getting the gene names and lengths the data is sorted by length. A rolling window is used to create bins. The user can change the size of the window as well as the step size of the window. 

## Prerequisites:

### Bioconductor packages:  
  - biomaRt  
```{} 
    source("https://bioconductor.org/biocLite.R")  
    biocLite("biomaRt")
```
  - edgeR  
```{}
    source("https://bioconductor.org/biocLite.R")  
    biocLite("edgeR")  
```
  - preprocessCore  
```{}
    source("https://bioconductor.org/biocLite.R")  
    biocLite("preprocessCore")
```  

###  CRAN packages:  
  - shiny  
```{}
    install.packages("shiny") 
```  
  - DT
```{}
    install.packages("DT") 
```
  - data.table
```{}
    install.packages("data.table") 
```
  - hash
```{}
    install.packages("hash") 
```
  
## Usage:

### LONGO():
The LONGO function allows the user to input the intitial variables to get a
result and then allows the user to alter some of the variables and see how 
they will change the results. 
```{}
  LONGO()
```

### LONGOcmd():
The LONGOcmd function will automatically write the output data files to your 
working directory. This can allow faster data analysis if you know the values
to use. 
```{}
   LONGOcmd("~/data.tsv")
   LONGOcmd("~/data.tsv", SEP = "\t")
   LONGOcmd("~/data.tsv", WINDOW_SIZE = 350, MULTI_PROBES = "mean", FILTERED = FALSE)
```


## BiomaRt identifier

```{r, echo=FALSE}
   biomaRt::listDatasets(biomaRt::useMart("ENSEMBL_MART_ENSEMBL", host = "www.ensembl.org"))[1]
```

```{r, echo=FALSE}
   biomaRt::listAttributes(biomaRt::useMart("ENSEMBL_MART_ENSEMBL", host = "www.ensembl.org",
                         dataset = "hsapiens_gene_ensembl"))[1]
```

## Output

### LONGO Data
show output data...

### LONGO Plot
show output plot

### JS Distance
show output plot








this is for my reference. will be removed,....


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
